\documentclass[11pt]{article}
% From the requirements: Font size to be used is Arial/11pt.
\usepackage{fontspec}
\usepackage{hyperref}
\usepackage{glossaries}
\setmainfont{Arial}
\makeglossaries

\newglossaryentry{Unity}
{
    name=Unity,
    description={Unity is a game development platform, can be used to make 3D environments. \url{http://unity3d.com/unity}}
}

\newglossaryentry{CleVR}
{
    name=CleVR,
    description={VR development team at Yes!Delft, focused on virtual reality therapy solutions. \url{http://clevr.net/}}
}

\begin{document}

\title{Architecture design (Draft)}
\author{
	Adriaan de Vos - addevos - 4422643\\
	Boris Schrijver - brschrijver - 4315332\\
	Carlos Brunal - cbrunal - 4002725\\
	Leon Hoek - ljhoek - 4021606\\
	Wim de With - wdewith - 4295277
}
\date{\today}

\maketitle

\newpage
\tableofcontents
\newpage

% 1. Introduction
\section{Introduction}
This document provides an overview of the system which will be built during the context project Health
Informatics for \gls{CleVR}. The architecture of the system will be explained in the form of high level components, sub-components and sub-systems. This document is a work-in-progress, it will be updated during the course of the project, each sprint. A final deliverable will be presented at the time the code is done.

    % 1.1 Design goals
    \subsection{Design goals}
    Throughout the project we will maintain design goals named; "Performance", "Ease of use" and "Extensibility". They'll be explained in each subsection respectively.

        \subsubsection{Performance}
        The existing technology runs at an frame rate of 90 frames per second. Each frame has just more than 10 ms to render. We, as the development team, should limit the time needed for each frame to update the map/world as much as possible to keep the program running smoothly. This is of vital importance to the treatment of the patients because any delay in performance may break immersion and cause nausea.
        
        \subsubsection{Ease of use}
       The interactive map should require little maintenance from the therapist during treatment. The focus of the therapist while giving treatment should be on the patient, not troubleshooting with the tools.
    It is important for the therapist to quickly see up-to-date information on the location of objects and actors in the \gls{Unity} world, as well as the moods of actors, the field of vision of the patient and more, to quickly determine triggers for the patients. It should also be quick and simple for the therapist to manipulate the environment according to those triggers. 
            
        \subsubsection{Extensibility}
        The software is to be implemented with future growth in consideration. The representatives of CleVR expressed the need for the software to be free of licensed libraries and also that it may be upgrade-able in the future. We at HiVr are making a foundation for future developers.


% 2. Software architecture views
\section{Introduction}
This section discusses the architecture of the system. We will briefly describe what each sub-system does, what the inter-dependencies are and how they work together. Research is currently being conducted and the following section will be updated accordingly.

    % 2.1 Subsystem decomposition (sub-systems and dependencies between them)
    \subsection{Subsystem decomposition}
    We are planning to build 3 components:
	\begin{itemize}
  		\item The graphical interface itself.
  		\item The needed plugin/protocol with Unity to let the GUI communicate with the Unity world.
        \item The needed network protocol to connect host and client computers
	\end{itemize}   
    
    % 2.2 Hardware/software mapping (mapping of sub-systems to processes and computers, communication between computers)
    \subsection{Hardware/software mapping }
    The tools we will use are the standard input devices for any computer, namely the keyboard and mouse. An optional hardware that we might implement is touchscreen integration. This is yet to be decided.
    Furthermore, the system will be running in 2 computers, on for the VR simulation and one to function as control panel for the therapist, these will be connected via a local network.
    
    % 2.3 Persistent data management (file/ database, database design)
    \subsection{Persistent data management (file/ database, database design)}
    The interact-able map being developed is a viewer for the world defined by Unity. Everything the viewer processes will be given to it at run-time, and as the work being done by Unity is out-of-scope for this context project. This project will therefore not include persistent data management.
    
    % 2.4 Concurrency (processes, shared resources, communication between processes, deadlocks prevention)
    \subsection{Concurrency}
    Each frame has just more than 10 ms to render. We should limit the time needed for each frame to update the map/world as much as possible to keep the program running smoothly. We discussed a window of 1ms to send and receive all our commands. 
    We still have to determine our lag limit, but ideally something low enough that the user itself wont notice. 
    
\newpage

\section{Glossary}
% 3. Glossary
\printglossary[title=]

\end{document}
